---
title: "Item hierarchies"
author: "Michael Hahsler"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Item hierarchies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(arules)
set.seed(1234)
```

Real data sets may contain many closely related items. A supermarket, for
example, may stock dozens of types of milk and hundreds of dairy products. An
item hierarchy maps these detailed items to broader groups, such as mapping
milk and yogurt to dairy. The hierarchy makes it possible to analyze patterns
at the category level.

Store each hierarchy level as a column in the transaction object's
`itemInfo()` data frame.

```{r}
trans <- transactions(list(
  T1 = c("apple", "banana"),
  T2 = c("apple", "yogurt"),
  T3 = c("banana", "milk"),
  T4 = c("apple", "banana", "milk"),
  T5 = c("milk", "yogurt"),
  T6 = c("apple", "banana", "yogurt")
))
itemInfo(trans)
```

Initially, `itemInfo()` contains only the item labels. Add `category` as one
level of the hierarchy.

```{r}
category_list <- c(
  apple = "fruit", banana = "fruit",
  milk = "dairy", yogurt = "dairy"
)
itemInfo(trans)$category <- category_list[itemLabels(trans)]
itemInfo(trans)
```

## Aggregating transactions

`aggregate()` replaces detailed items with their groups. Multiple items from
the same group in one transaction become a single group item.

```{r}
by_category <- aggregate(trans, by = "category")
inspect(trans)
inspect(by_category)
itemFrequency(by_category)
```

Mine the aggregated transactions when the analysis should operate only at the
group level. Mining again calculates valid quality measures for that level.

```{r}
category_rules <- apriori(
  by_category,
  parameter = list(support = 0.3, confidence = 0.5, minlen = 2),
  control = list(verbose = FALSE)
)
inspect(category_rules)
```

## Mine across hierarchy levels

`addAggregate()` retains the detailed items and adds their group items. By
default, an asterisk marks group items. The resulting transactions can produce
rules that cross hierarchy levels.

```{r}
multilevel <- addAggregate(trans, by = "category")
inspect(multilevel)

multilevel_rules <- apriori(
  multilevel,
  parameter = list(support = 0.1, confidence = 0.6, minlen = 2),
  control = list(verbose = FALSE)
)
multilevel_rules
```

Adding category items creates trivial rules such as `{apple} => {fruit*}`
because the hierarchy guarantees them. `filterAggregate()` removes rules that
contain both a detailed item and its own aggregate, reducing the rule set and
making it easier to interpret.

```{r}
multilevel_rules <- filterAggregate(multilevel_rules)
multilevel_rules

inspect(sort(multilevel_rules, by = "lift"))
```
