---
title: "Using arules with tidyverse"
author: "Michael Hahsler"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Interest measures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(arules)
set.seed(1234)
```

`arules` works seamlessly with [tidyverse](https://tidyverse.org/). For example:

* `dplyr` can be used for cleaning and preparing the transactions.
* `transactions()` and other functions accept `tibble` as input.
* Functions in arules can be connected with the pipe operator `|>`.
* [arulesViz](https://mhahsler.github.io/arulesViz) provides visualizations based on `ggplot2`.

For example, we can remove the ethnic information column before creating transactions and then mine and inspect rules.
```{r }
library("tidyverse")
library("arules")
data("IncomeESL")

trans <- IncomeESL |>
  select(-`ethnic classification`) |>
  transactions()
rules <- trans |>
  apriori(
    supp = 0.1, conf = 0.9, target = "rules",
    control = list(verbose = FALSE)
  )
rules |>
  head(3, by = "lift") |>
  as("data.frame") |>
  tibble()
```
